Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-08-18 paper/paper.tex
more refs on MDPs in algorithmic trading

\begin{mdframed}
\paragraph*{Why MDPS ?} At this point, it is righteous to question the applicability of MPDs as a model for something as complex as human behavior.
Indeed a critique could argue that Markov chains are state-machines without memory. These may describe insects, or other behaviorally primitive beings like ATM machines, insects, etc., but won't be sufficient to describe human beings, as for example, human behavior is heavily influenced not only by the current state but by past states as well (memory).

@@

\item Successes in AI/ML: \citep{ng2004,abbeel2004,mnih2015,silver2016mastering,pritzel2017neural}

\end{itemize}
\end{mdframed}

>>>>

% \begin{mdframed}
\paragraph*{Why MDPs ?} At this point, it is righteous to question the applicability of MPDs as a model for something as complex as human behavior.
Indeed a critique could argue that Markov chains are state-machines without memory. These may describe insects, or other behaviorally primitive beings like ATM machines, insects, etc., but won't be sufficient to describe human beings, as for example, human behavior is heavily influenced not only by the current state but by past states as well (memory).

@@

\item Successes in AI/ML:
  \begin{itemize}
    \item Robotics: \citep{ng2004,abbeel2004}
    \item Games and other: ~\citep{mnih2015,silver2016mastering,pritzel2017neural}
\end{itemize}

  \item Algorithmic trading. In financial trading, the main actions which the agent (human or computer acting on behalf of a human operator) must execute strategically are: sell (sell a given quantity of a commodity), buy (by a given quantity of a commodity), do nothing. According to how the market responds, a definite gain / loss is recorded as a consequence of the executed action, perhaps with some delay. Over the years, research in algorithmic trading has identified MDPs as a powerful framework for modelling this behavioral process  ~\citep{brazdil2017,yang15,yang14,yang12,dempster2006,hult2010}, for which dynamic-programming based algorithms can be employed to produce numerical solutions. ~\citep{abergel2017} is an excellent reference with the mathematical details on how MDPs work in finance.

\end{itemize}
% \end{mdframed}
